### 2012-11-17 inst/examples/mult_uncertainty_test.Rmd
successful example of implementation uncertainty

    ## Initialize stuff
    sigma_g <- sigmas['sigma_g']      
    sigma_m <- sigmas['sigma_m']
    sigma_i <- sigmas['sigma_i']
    n_x <- length(x_grid)
    n_h <- length(h_grid)
    D <- matrix(NA, nrow=n_x, ncol=Tmax)

@@

    # integrate over uncertainty in I and X 
    F <- lapply(1:n_h, function(q){  
      t(sapply(1:n_x, function(y){
        out <- numeric(n_x)
        mu <- sum(sapply(1:n_x, function(x)
          f(x_grid[x],h_grid,p) %*% I[q,] *  M[x,y])) # Implementation & Measurement error
        if(mu==0)
          out[1] <- 1
        else 
          out <- dlnorm(x_grid/mu, 0, sigma_g)
        out/sum(out)
      }))
    })

    Ep <- M %*% P %*% I
    V <- Ep
    for(t in 1:Tmax){
      D[,(Tmax-t+1)] <- apply(V, 1, which.max)
      v_t <- apply(V, 1, max) # vector of current values
      V <- sapply(1:n_h, function(j){ # updated value matrix
        Ep[,j] + (1-delta) * M %*% F[[j]] %*% v_t
      })
    }
    list(D=D, M=M, I=I, P=P, Ep=Ep, V=V, F=F)
}

>>>>

Tmax = 25
sigmas =c (sigma_g=.3, sigma_m=0.3, sigma_i=0.3)

    sigma_g <- sigmas['sigma_g']      
    sigma_m <- sigmas['sigma_m']
    sigma_i <- sigmas['sigma_i']
    n_x <- length(x_grid)
    n_h <- length(h_grid)
    D <- matrix(NA, nrow=n_x, ncol=Tmax)

@@

    # integrate over uncertainty in I and X 
    F <- lapply(1:n_h, function(q){  
      t(sapply(1:n_x, function(y){
        out <- numeric(n_x)
        mu <- sum(sapply(1:n_x, function(x)
          f(x_grid[x],h_grid,p) %*% I[q,] *  M[y,x])) # Implementation & Measurement error
        if(mu==0)
          out[1] <- 1 ## Wow, really? should we be applying noise to the f*I*M product or the f?  
        else 
          out <- dlnorm(x_grid/mu, 0, sigma_g)
        out/sum(out)
      }))
    })

    Ep <- M %*% P %*% t(I)
    V <- Ep
    for(t in 1:Tmax){
      D[,(Tmax-t+1)] <- apply(V, 1, which.max)
      v_t <- apply(V, 1, max) # vector of current values
      V <- sapply(1:n_h, function(j){ # updated value matrix
        Ep[,j] + (1-delta) * M %*% F[[j]] %*% v_t
      })
    }
    list(D=D, M=M, I=I, P=P, Ep=Ep, V=V, F=F)
}
